\newglossaryentry{RS-232}{
  name={RS-232},
  description={An electrical (physical level) protocol used to communicate data in chunks of up to 8 bits. The protocol is asynchronous in that it does not use a line dedicated for the clocking of the data; the \gls{baud-rate} must be communicated out-of-band. Refer to \textcite[Section 14.7.8]{art}.}
  }
\newglossaryentry{token}{
  name={token},
  description={A component of Rust source code. A single token could for example be an identifier or a group of other tokens.}
  }
\newglossaryentry{sample-rate}{
  name={sample rate},
   description={The frequency at which a control system such as a \gls{regulator} samples sensor input and manipulates the system via its actuators.}
  }
\newglossaryentry{downstream}{
   name={downstream},
  description={In software development the dependencies of code is often compared to that of a stream of water. A program commonly depends on libraries. This program is then downstream of the libraries; just as water flows downstream, code from these libraries flow downstream into the dependent program. Opposite of \gls{upstream}. The comparison also holds for data dependency.}
  }
\newglossaryentry{upstream}{
  name={upstream},
  description={Opposite of \gls{downstream}: the library or data is upstream from the program or concerning software component.}
  }
\newglossaryentry{frontend}{
  name={frontend},
  description={User-facing software that maintains a connection with a \gls{backend}. May also be referred to as a \gls{client}.}
}
\newglossaryentry{client}{
  name={client},
  description={A \gls{frontend}.}
}
\newglossaryentry{backend}{
  name={backend},
  description={Software that serves a \gls{frontend}. Also referred to as a \gls{daemon}.}
}
\newglossaryentry{daemon}{
  name={daemon},
  description={A program that runs in the background responsible for a task that does not have a defined execution time (runs continually). An example of a daemon is a web server which serves \glspl{client}. Sometimes also referred to as a \gls{backend}.}
}
\newglossaryentry{JSON}{
  name={JSON},
  description={``A text syntax that facilitates structured data interchange between all programming languages'' \parencite{json}. \acrfull{JSONacr} is an interchange format that is both machine and human-readable.}
}
\newacronym{JSONacr}{JSON}{{JavaScript Object Notation}}
\newglossaryentry{cdylib}{
  name={cdylib \gls{crate}},
  description={A crate that specifies \texttt{crate\_type = ["cdylib"]} in \texttt{Cargo.toml}. Upon building the crate a dynamic library (a shared object file) that targets the stable C \gls{ABI} is generated. Additionally, it is trivial to find the file location of cdylibs with \texttt{cargo} which is not the case with non-cdylibs crates that instead target the less stable Rust ABI. The only way to directly generate a shared object file via \texttt{cargo}, as of writing, is by building a dylib or a cdylib.}
}
\newacronym{ABI}{ABI}{{Application Binary Interface}}
\newglossaryentry{JTAG}{
  name={JTAG},
  description={An industry standard that, among other features, offers the ability to program an \gls{MCU} \parencite[Section 14.7.4]{art}.}
}
\newglossaryentry{SWD}{
  name={Serial Wire Debug},
  text={SWD},
  description={A debug port used for programming and debugging an \gls{MCU} \parencite{coresight}.}
}
\newglossaryentry{manglfn}{
  name={mangled function},
  description={When Rust code is compiled its function are mangled in order to allow two functions in different namespaces (e.g., \texttt{mod app \{ ... \}} and \texttt{mod aux \{ ... \}}) to have the same name. Aside from namespace information, mangling is also used to describe argument and return type information. This added information adds complexity when resolving the function in a shared object as a result of building a \gls{cdylib}. When mangling is disabled for a function, its name can be directly resolved in the shared object, but its name must be unique in that object.}
  }
\newglossaryentry{envvar}{
  name={environmental variable},
  description={A string variable that exists in the environment that programs execute. A change to an environmental variable can change how programs are executed and can be seen as a complement to program arguments.}
  }
  \newglossaryentry{regulator}{
  name={regulator},
  description={A control system used to track one or more reference signals. The regulator observes (either directly or by approximation) the \gls{system-state} via sensors and affect it via actuators.}
  }
\newglossaryentry{stdout}{
  name={\texttt{stdout}},
  description={The standard output of a running program. For example, a ``Hello, World!''-program will write ``Hello, World'' to the standard output.}
  }
\newglossaryentry{sigint}{
  name={SIGINT handler},
  description={A function that executes when the program receives a SIGINT \gls{signal}.}
}
\newglossaryentry{signal}{
  name={POSIX signal},
  description={An asynchronous notification sent to a program by the operating system, meant to trigger specific behavior \parencite[Section 7.5.1]{burns}. Examples or such signals are SIGINT (``interrupt''; on reception the program should terminate) and SIGHUP (``hang up'').},
}
\newglossaryentry{thread}{
  name={thread},
  description={A unit of concurrency available in rich operating systems used to execute multiple function simultaneously.}
  }
\newglossaryentry{task}{
  name={task},
  description={A unit of concurrency \parencite[Section 4.1]{burns}. In this text, a task specifically refers to an \acrshort{RTIC} task (\cref{rtic}).}
}
\newglossaryentry{hardware-task}{
  name={hardware task},
  description={A \gls{task} scheduled by hardware. Bound to an \gls{interrupt}.}
}
\newglossaryentry{software-task}{
  name={software task},
  description={A \gls{task} scheduled by software. Not exclusively bound one-to-one to an \gls{interrupt}.}
}
\newglossaryentry{interrupt}{
  name={interrupt},
  description={A hardware resource, a request to which can be requested and subsequently scheduled by hardware, upon which a \gls{hardware-task} executes. An interrupt is the most efficient method for an \gls{MCU} to react to external stimuli (e.g., by pressing a button). Can also be referred to as an \gls{IRQ}.}
}
\newglossaryentry{socket}{
  name={socket},
  description={TODO}
}
\newglossaryentry{probe}{
  name={probe},
  description={Dedicated debugging hardware. Acts as the interface between the host system and the target \gls{MCU}.}
}
\newglossaryentry{task-dispatcher}{
  name={task dispatcher},
  description={\Gls{software-task} scheduler and executor abstracted upon an \gls{interrupt} handler and thus effectively a \gls{hardware-task} hidden for the user. The task dispatcher keeps tabs on when software tasks should be executed.}
}
\newglossaryentry{tracing}{
  name={tracing},
  description={The act of acquiring continuous insight into the system with various levels of granularity. Tracing can for example yield information about what is being executed, when, for how long, with what data, and using what intructions.}
}
\newglossaryentry{data-tracing}{
  name={data tracing},
  description={\Gls{tracing}, specifically regarding what data is being computed in the system.},
}
\newglossaryentry{exception-tracing}{
  name={exception tracing},
  description={\Gls{tracing}, specifically regarding what \gls{exception} are being handled.},
}
\newglossaryentry{exception}{
  name={exception},
  description={An \gls{interrupt}.},
}
\newglossaryentry{hardare-event-packet}{
  name={hardware event packet},
  description={A \gls{trace-packet} describing a hardware event, such as memory being written to or an \gls{interrupt} handler being executed.},
}
\newglossaryentry{watch-address}{
  name={watch address},
  description={Memory address which the \gls{DWT} monitors for changes. When the memory at this address is written to a \gls{hardware-event-packet} is generated, presuming appropriate configuration has been previously applied.}
}
\newglossaryentry{watch-variable}{
  name={watch variable},
  description={In-memory variable from which a \gls{watch-address} is derived.}
}
\newglossaryentry{system-clock}{
  name={system clock},
  description={A clock which drives (a potentially partial component) of the \gls{MCU}. The frequency of this clock is the frequency at which instructions of the \gls{user-application} are executed.}
}
\newglossaryentry{user-application}{
  name={user application},
  description={An \Gls{RTIC} application that is flashed and executed on the \gls{MCU}.}
}
\newglossaryentry{baud-rate}{
  name={baud rate},
  description={The speed at which a \gls{RS-232} connection communicates; equivalent to bits per second. \parencite[Section 14.7.8]{art}}
}
\newglossaryentry{crate}{
  name={crate},
  description={A Rust unit of compilation and linking. A crate usually contains libraries and programs written in Rust.}
}
\newglossaryentry{enum}{
  name={enum},
  description={An enumerated type.}
}
\newglossaryentry{struct}{
  name={struct},
  description={A product of other types.}
}
\newglossaryentry{macro}{
  name={macro},
  description={A declarative Rust functionality extension. Either function-like, or modifies compiled code by operating on \glspl{token} when applied.}
}
\newglossaryentry{manifest}{
  name={crate manifest},
  description={The \gls{crate}'s \texttt{Cargo.toml} file.}
}
\newglossaryentry{feature}{
  name={crate feature},
  description={An optional feature-set of a \gls{crate}.}
}
\newglossaryentry{trait}{
  name={trait},
  description={An abstract interface types can implement. A feature that enables code base modularity and composability.}
}
\newglossaryentry{trace-stream}{
  name={trace stream},
  description={A continuous stream of \glspl{trace-packet}.}
}
\newglossaryentry{trace-packet}{
  name={trace packet},
  description={A \gls{ITM} or \gls{DWT} protocol packet. Refer to \textcite[Part~D4]{arm-rm}.}
}
\newglossaryentry{hardware-event-packet}{
  name={hardware event packet},
  description={\Gls{trace-packet}, specifically one from the \gls{DWT}.},
}
\newglossaryentry{safe}{
  name={safe},
  description={Rust code that is not \gls{unsafe}.}
}
\newglossaryentry{unsafe}{
  name={unsafe},
  description={Context in which Rust code can potentially violate its memory-safety rules.}
}
\newglossaryentry{prescaler}{
  name={prescaler},
  description={A clock divider. For example, a clock frequency of $16~\text{MHz}$ prescaled by $2$ yields a frequency of $8~\text{MHz}$.}
}
\newglossaryentry{overhead}{
  name={overhead},
  description={Necessary work that must be done to enable functionality or start a process (such as emitting trace packets).}
}
\newglossaryentry{real-time}{
  name={real-time system},
  text={real-time},
  description={Any system which must respond to externally generated input stimuli, or perform a periodic (or aperiodic) function, within a finite and specified period \parencite[Chapter 1.1]{burns}.}
}
\newglossaryentry{system-state}{
  name={system state},
  description={A set of variables that describe a system; e.g., the velocity and acceleration of a vehicle.}
}
\newglossaryentry{microcontroller-unit}{
  name={microcontroller unit},
  description={A \gls{CPU} combined with a set of peripherals such as voltage sensors, serial communication interfaces, volatile and non-volatime memory.}
}

\newabbreviation{UTID} {UTID} {{Unique Task Identifier}}
\newabbreviation{PC} {PC} {{Program Counter}}
\newabbreviation{CPU} {CPU} {{Central Processing Unit}}
\newabbreviation{MCU} {MCU} {{\Gls{microcontroller-unit}}}
\newabbreviation{SWO} {SWO} {{Serial Wire Out}}
\newabbreviation{RTIC} {RTIC} {{\Gls{real-time} \Gls{interrupt}-Driven Concurrency}}
\newabbreviation{FIFO} {FIFO} {{First-In, First-Out}}
\newabbreviation{RTOS} {RTOS} {{\Gls{real-time} Operating System}}
\newabbreviation{SRP} {SRP} {{Stack Resource Policy}}
\newabbreviation{DCB} {DCB} {{Debug Control Block}}
\newabbreviation{SCS} {SCS} {{System Control Space}}
\newabbreviation{SCB} {SCB} {{System Control Block}}
\newabbreviation{DCB_DEMCR} {DEMCR} {{Debug Exception and Monitor Control Register}}
\newabbreviation{ITM} {ITM} {{Instrumentation Trace Macrocell}}
\newabbreviation{TPIU} {TPIU} {{Trace Port Interface Unit}}
\newabbreviation{DWT} {DWT} {{Data Watchpoint and Trace}}
\newabbreviation{ETB} {ETB} {{Embedded Trace Buffer}}
\newabbreviation{WCET} {WCET} {{Worst Case Execution Time}}
\newabbreviation{EDF} {EDF} {{Earliest Deadline First}}
\newabbreviation{PAC} {PAC} {{Peripheral Access Crate}}
\newabbreviation{HAL} {HAL} {{Hardware Abstraction Layer}}
\newabbreviation{API} {API} {{Application Programming Interface}}
\newabbreviation{TPIU_ACPR} {TPIU\_ACPR} {{Asynchronous Clock Prescaler Register}}
\newabbreviation{ETM} {ETM} {{Embedded Trace Macrocell}}
\newabbreviation{DWT_CTRL} {DWT\_CTRL} {{Control Register}}
\newabbreviation{TPIU_TYPE} {TPIU\_TYPE} {{TPIU Type Register}}
\newabbreviation{ITM_TCR} {TPIU\_TCR} {{Trace Control Register}}
\newabbreviation{RAZ-WI} {RAZ/WI} {{Read-As-Zero, Writes Ignored}}
\newabbreviation{RAZ} {RAZ} {{Read-As-Zero}}
\newabbreviation{RAO} {RAO} {{Read-As-One}}
\newabbreviation{DWT_FUNCTIONn} {DWT\_FUNCTION$n$} {{Comparator Function registers}}
\newabbreviation{SBZ} {SBZ} {{Should-Be-Zero}}
\newabbreviation{DWT_COMPn} {DWT\_COMP$n$} {{Comparator registers}}
\newabbreviation{DWT_MASKn} {DWT\_MASK$n$} {{Comparator Mask registers}}
\newabbreviation{AST} {AST} {{Abstract Syntax Tree}}
\newabbreviation{TLV} {TLV} {{Type-Length-Value}}
\newabbreviation{GTS1} {GTS1} {{Global timestamp packet format 1}}
\newabbreviation{GTS2} {GTS2} {{Global timestamp packet format 2}}
\newabbreviation{LTS1} {LTS1} {{Local timestamp packet format 1}}
\newabbreviation{LTS2} {LTS2} {{Local timestamp packet format 2}}
\newabbreviation{IPSR} {IPSR} {{\Gls{interrupt} Program Status Register}}
\newabbreviation{USB} {USB} {{Universal Serial Bus}}
\newabbreviation{IRQ} {IRQ} {{\Gls{interrupt} Request}}
\newabbreviation{RFC} {RFC} {{Request for Comments}}
\newabbreviation{CSV} {CSV} {{Comma Separated Values}}
\newabbreviation{WG} {WG} {{Working Group}}
\newabbreviation{IC} {IC} {{Integrated Circuit}}


\newglossaryentry{armv7-m}{
  name={ARMv7-M},
  description={An \gls{MCU} architecture, specified in \textcite{arm-rm}.}
}
\newglossaryentry{header}{
  name={header}, %% packet header?
  description={TODO}
}

\newglossaryentry{payload}{
  name={payload},
  description={TODO}
}
\newglossaryentry{quality}{
  name={quality}, %% timestamp quality
  description={TODO}
}
\newglossaryentry{data-trace-packet}{
  name={data trace packet},
  description={TODO}
}
\newglossaryentry{family}{
  name={\gls{MCU} family},
  text={family},
  description={A set of \glspl{MCU} that share characteristics, such as the underlying architecture. Members of a family can differ in terms of memory density and/or peripheral availability, for example.}
}
\newglossaryentry{peripheral}{
  name={peripheral},
  description={TODO}
}
\newglossaryentry{register-field}{
  name={register field},
  description={TODO}
}
\newglossaryentry{artifact}{
  name={artifact},
  description={TODO}
}
\newglossaryentry{git-revision}{
  name={git revision},
  description={TODO}
}
\newglossaryentry{unknown-bind}{
  name={unknown bind},
  description={An \gls{IRQ} which cannot be directly associated with an \gls{RTIC} \gls{task} event.}
}
\newglossaryentry{known-bind}{
  name={known bind},
  description={An \gls{IRQ} which can be directly associated with an \gls{RTIC} \gls{task} event.}
}
